\documentclass[A4]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/jeff999955}{\Large Jeff Tseng}} & Email : \href{mailto:jeff999955@gmail.com}{jeff999955@gmail.com}\\
  & GitHub: \href{https://github.com/jeff999955}{jeff999955} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National Taiwan University}{\textit{GPA 3.92/4.0}}
{Bachelor of Science in Computer Science and Information Engineering}{2019 -- 2023}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Research and Teaching Experience}
\resumeSubHeadingListStart

\resumeSubheading
{NTU CSIE Network Administration and System Administration}{Taipei, Taiwan}
{Lead of Wired Network Team}{2022 - 2023}
\begin{itemize}
  \item Developed daily log synchronization tools integrated with Google Spreadsheet.
  \item Created a network infrastructure parser and visualization toolkit.
  \item Led junior members to complete a project on command line interface for HP switch.
\end{itemize}

\resumeSubheading
{Deep Learning for Computer Vision (DLCV)}{Taipei, Taiwan}
{Teaching Assistant}{2022 Fall}
\begin{itemize}
  \item Designed assignment questions and held dedicated TA hours.
\end{itemize}

\resumeSubheading{Vision \& Language Lab (VLLab)}{Taipei, Taiwan}{Undergraduate Research Student}{2022}
\begin{itemize}
  \item  Researched on different training scenarios for \textbf{text-guided image manipulation}.
\end{itemize}

\resumeSubheading{Communications \& Multimedia Lab (CMLab)}{Taipei, Taiwan}{Undergraduate Research Student}{2022}
\resumeItemListStart
\resumeItem{Orbeez-SLAM}{Research paper accepted by ICRA 2023}
\resumeItemListEnd

\resumeSubheading
{Miulab}{Machine \& Intelligence Understanding Lab}
{Undergraduate Research Student}{2021 Fall - 2022 Spring}
\begin{itemize}
  \item Researched on enhancing Automatic Speech Recognition (ASR) and Spoken Language Understanding through natural language pretraining.
  \item Arranged \textbf{over 20 cross-modal (text and speech) tasks}, their benchmarks, and datasets.
\end{itemize}

\resumeSubheading
{Data Structure and Algorithms}{}
{Teaching Assistant}{2021 Spring}
\begin{itemize}
  \item Designed activity about data structure with Kahoot and online judge platform.
\end{itemize}

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-------------
\section{Publication}
\resumeSubHeadingListStart
\resumeSubheading
{Orbeez-SLAM}{CMLab}{A Real-time Monocular Visual SLAM with ORB Features and NeRF-realized Mapping}{2022/09}
\begin{itemize}
  \item Accepted by ICRA 2023.
  \item Used \textbf{CUDA \& C++} to migrate instant-ngp NeRF to ORB-SLAM to achieve \textbf{3D scene reconstruction} with \textbf{800x speedup} over other NeRF-based SLAMs.
  \item Achieved better reconstruction quality and more precise localization and mapping (lower ATE).
\end{itemize}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Side Projects}
\begin{itemize}
  \item \textbf{Coughvid}: Integrated audio models by Pytorch for cough detection and linear models for clinical data to a Flask API designed for COVID-19 cough detection.
  \item \textbf{Japanese Memorizer App}: Developed a vocabulary learning mobile application with Flutter, bloc, firebase backend, and the CI/CD pipeline on codemagic.
  \item \textbf{nvtop modification}:  Added user filtering feature, in C, to an open-source GPU monitoring tool - nvtop.
\end{itemize}

%-----------EMPLOYMENT HISTORY-----------------
\section{Employment History}

\resumeSubHeadingListStart

\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{GoGoX} & Taipei, Taiwan \\
  \textit{\small Software Engineer, Data Scientist} & \textit{\small Jun, 2023 - present} \\
  \textit{\small Data Scientist Intern} & \textit{\small Sep, 2022 - Jun, 2023} \\
\end{tabular*}\vspace{-5pt}

\resumeItemListStart
\resumeItem{Working Time Labeling}
{}
\begin{itemize}
  \item Develop an \textbf{ML algorithm} with \textbf{feature selection} on label driver GPS data and order data to \textbf{automate the labeling process} of pickup and arriving time.
  \item \textbf{Identify the anomaly} behavior of driver with \textbf{autoencoder} to help filter out cases unsuitable for labeling model.
  \item \textbf{Analyze the correlation} between GPS data and order data to explore room for improvement.
\end{itemize}

\resumeItem{GPS Map Matching}{}
\begin{itemize}
  \item Build the driver travel time database to improve pick up estimation model and order working time model.
  \item Use \textbf{Python shapely} to map GPS point to most probable road segment on \textbf{OpenStreetMap}.
  \item Find the route with {Hidden Markov Model} with \textbf{Python} given possible road segments.
  \item Validate correctness of the algorithm by visualizing \textbf{OpenStreetMap} and GPS track with \textbf{Python folium}.
\end{itemize}

\resumeItem{GoGoX QA Bot}{}
\begin{itemize}
  \item Design the pipeline based on \textbf{OpenAI}, \textbf{Pinecone}, and \textbf{Langchain} to support \textbf{customized  ChatGPT} with \textbf{prompt engineering}.
  \item Ingest the customer service data to \textbf{Pinecone} as the \textbf{vector database}, the knowledge base of the ChatBot.
  \item Expose the ChatBot as API and web interface on \textbf{Google Cloud}.
\end{itemize}
\resumeItemListEnd

\resumeSubheading
{ASUS Intelligence Cloud Service}{Taipei, Taiwan}
{Software Engineering Intern}{Jul 2022 - Sep 2022}
\resumeItemListStart
\resumeItem{Selenium IDE Modification}
{}
\begin{itemize}
  \item Add popup menu to original IDE with \textbf{Electron} and \textbf{NodeJS} to support additional functions and \textbf{facilitate the testing} phase.
  \item \textbf{Eliminate 19} out of \textbf{23} testcases that is unable to be automatically recorded with \textbf{our modified Selenium}.
\end{itemize}
\resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}